---
title: "youtubeR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part One


```{r }
#install.packages(c("igraph","digest","rgl","httr","rcurl","jsonlite"))

library(igraph)
library(digest)
#library(rgl)
library(httr)
library(RCurl)
library(dplyr)
library(jsonlite)
```

## Read CSV

Here we read the csv into a dataframe & build graph g

```{r }
ga.data <- read.csv('ga_edgelist.csv', header = T)
g <- graph.data.frame(ga.data,directed = F)
```

## Centrality 

we build a dataframe with each metric

```{r }
gb <- betweenness(g)
gc <- closeness(g)
ge <- eigen_centrality(g)$vector

a <- as.data.frame(as.vector(gb))
a <- cbind(a,as.vector(ge))
a <- cbind(a,as.vector(gc)) 
a <- cbind(a,names(ge)) 

colnames(a) <- c("betweenness","closeness","eigen_centrality","names")

a
```

## Finding maximal vlues


```{r }

  a <- a %>%
    mutate(mxgb = ifelse(betweenness==max(betweenness),1,0),
           mxgc = ifelse(closeness==max(closeness),1,0),
           mxge = ifelse(eigen_centrality==max(eigen_centrality),1,0)) 

```


## Max Betweenness

```{r }
 a %>% 
  filter(mxgb==1) %>%
  select(names,betweenness)
```

## Max closeness



```{r }
 a %>% 
  filter(mxgc==1) %>%
  select(names,closeness)
```
## Max eigen_centrality

```{r }
 a %>% 
  filter(mxge==1) %>%
  select(names,eigen_centrality)
```

## Run community algorithms

Edge betweenness and sizes of its 7 groups

```{r }
gc <-  edge.betweenness.community(g)


sizes(gc)
```



Fastgreedy and and sizes of its 6 groups

```{r }

gc2 <- fastgreedy.community(g)

sizes(gc2)
```

## Plot of Edge betweenness

```{r }
plot(g, vertex.size=5, vertex.label=names(g),
     vertex.color=membership(gc), asp=FALSE)
```

## Plot of Fastgreedy



```{r }
plot(g, vertex.size=5, vertex.label=names(g),
     vertex.color=membership(gc2), asp=FALSE)
```
## Edge betweenness modularity

```{r }
max(gc$modularity)


```

## Fastgreedy modularity



```{r }
max(gc2$modularity)
```
## Part Two

Here we crawl youtube for channels and subscriptions, each channel has several subscribtions which are 
themselves channels. The relation between a channel and a subscription would be our edge, the channels are
our vertices. 

```{r }
#  API key obtained via https://console.developers.google.com/ 
API_key='AIzaSyAkrLrCEIpS8s-GMMuz31SEM8Yx7ukv5W8'

# Base URL for Google API's services and YouTube specific API's
Base_URL='https://www.googleapis.com/youtube/v3'

# YouTube Web Services



YT_Service <- c( 'search?part=snippet&q=%s&type=%s&key=%s',                         # search API
                 'subscriptions?part=snippet,contentDetails&channelId=%s&key=%s&maxResults=15'    # subscriptions API
)


# here is the initial channel from which we crawl
cId <- 'UC74nY8aA7H3OWPRHJz6bUCQ'
```


## Crawling phase

set up the url

```{r }
url <- paste0(Base_URL, "/", sprintf(YT_Service[2], cId, API_key))
```

## read json

```{r }
result <- jsonlite::fromJSON(txt=url)
```



A list of subscription for the channel

```{r }
result$items$snippet$title
```

## build an initial dataframe for channels and subscriptions

```{r }
names <- as.list(result$items$snippet$title)
df <- as.data.frame(result$items$snippet$title)
df$col2 <- "MYNAME"
colnames(df) <- c("subscribtions","channel")

df
```



keep a list of channelIds for the crawling phase

```{r }
cIds <- as.list(result$items$snippet$resourceId$channelId)
```

## Crawler function

```{r }
crawl <- function(df,idx){
  url2 <- paste0(Base_URL, "/", sprintf(YT_Service[2], cIds[[idx]][1], API_key))
  result2 <- jsonlite::fromJSON(txt=url2)
  cName <- lapply(1:length(result2$items$snippet$title), function(j) names[[idx]][1])
  cName <- as.data.frame(unlist(cName))
  dft <- as.data.frame(result2$items$snippet$title)
  dft <- cbind(dft,cName)
  colnames(dft) <- c("subscribtions","channel")
  return(dft)
}
```



keep a list of crawled channels

```{r }
dfs <- lapply(c(1,3:6,8,10:13), function(x) crawl(df,x))
```

## A new dataframe full of channels and subscriptions, ready for the graph

```{r }
df2 <- do.call(rbind,dfs)
df <- rbind(df,df2)
colnames(df) <- c("from","to")

head(df)
```

## Build the graph



```{r }
gf <- graph.data.frame(df,directed = F)
```



## Centrality metrics

```{r }
gfb <- betweenness(gf)
gfc <- closeness(gf)
gfe <- eigen_centrality(gf)$vector

a2 <- as.data.frame(as.vector(gfb))
a2 <- cbind(a2,as.vector(gfe))
a2 <- cbind(a2,as.vector(gfc)) 
a2 <- cbind(a2,names(gfe)) 

colnames(a2) <- c("betweenness","closeness","eigen_centrality","names")

a2
```

preparations

```{r }

  a2 <- a2 %>%
    mutate(mxgfb = ifelse(betweenness==max(betweenness),1,0),
           mxgfc = ifelse(closeness==max(closeness),1,0),
           mxgfe = ifelse(eigen_centrality==max(eigen_centrality),1,0)) 

```


## Max betweenness

```{r }
 a2 %>% 
  filter(mxgfb==1) %>%
  select(names,betweenness)
```

## Max closeness



```{r }
 a2 %>% 
  filter(mxgfc==1) %>%
  select(names,closeness)
```

## Max eigen_centrality

```{r }
 a2 %>% 
  filter(mxgfe==1) %>%
  select(names,eigen_centrality)
```

## Community algos

edge.betweenness and sizes of the 9 groups

```{r }
gc3 <-  edge.betweenness.community(gf)


sizes(gc3)
```



fastgreedy.community and sizes of its 9 groups

```{r }

gc4 <- fastgreedy.community(gf)

sizes(gc4)
```

## edge betweenness graph

```{r }
plot(gf, vertex.size=5, vertex.label=names(gf),
     vertex.color=membership(gc3), asp=FALSE)
```

## fastgreedy.community graph

You can also embed plots, for example:

```{r }
plot(gf, vertex.size=5, vertex.label=names(gf),
     vertex.color=membership(gc4), asp=FALSE)
```
## edge betweenness modularity

```{r }
max(gc3$modularity)


```

## greedy modularity

You can also embed plots, for example:

```{r }
max(gc4$modularity)
```